---
title: "Homework #1 -- Pet Names Dataset"
author: "FATIMAH YOUSEF"
date: "`r Sys.Date()`"
output: github_document
---

**Student ID:2201002709**

**Deadline:** 23:59 on Saturday, 13 February 2021

**Total Points:** 30


## Loading Packages

```{r load-packages, message = FALSE}

library(tidyverse)
library(openintro)
library(ggrepel)
```


##Exercises

`1. 

(4 points)
```{r}

```
522519
2.

(4 points)

```{r}

```
variables = 7

3. 
(4 points)

```{r}

```
NA 483
Lucy 439
Charlle 387
Luna 355

`4.

(10 points)

```{r species-name-top5, eval=TRUE}
seattlepets %>%
group_by(species) %>%
count(animal_name, sort = TRUE) %>%
slice_max(n, n = 5) %>% arrange(species,n)
```

`5.  What names are more common for cats than dogs? The ones above the line or the ones below the line?

Oliver and Lily

(4 points)

`6. Is the relationship between the two variables (proportion of cats with a given name and proportion of dogs with a given name) positive or negative? What does this mean in context of the data?

Positive , if dogs name increase the cats names increase also and also if dogs name Decrease the cats name Decrease also in the same name of them.

(4 points)